Dataset of operator-client dialogues aligned with knowledge-base queries

### 2016-06-28 paper.tex
Update on Overleaf.
dataset description

\maketitle

\OP{Fill missing values about the dataset collected so far} \\
\OP{describe the dataset,apologize for not having the dataset collected - promise for camera ready version.} \\
\OP{grammar check} \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
We present a new dataset of human-human task-oriented conversations in the restaurant info domain for supervised training of autonomous systems. Currently, the dataset contains only \OP{XY} dialogues because we are still collecting more data, but we estimate that until camera ready deadline we will have more than seven hundreds dialogues. 
We aim at representing the conversation in such way that it is easy to train a system to replace an operator who provides information about the restaurants to clients.
In contrast to previously released datasets, our dataset contains easy to collect high-quality transcriptions of the client and operator actions during conversations.
We introduce a~very little overhead by collecting database calls in addition to the transcription of the conversation. 
In fact, we mimic very closely a~real situation in call centers where operators searches for answers through database user interface. 
On the other hand, just logging the calls to the task database provide us with information of the similar quality as it is contained in manually annotated dialogue state, just not annotated incrementally after each turn.
Tracking the database calls in task oriented systems together with conversation transcription should not introduce much overhead during data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.

@@

We used exactly the same database as provided for the DSTC2 challenge~\cite{henderson2014dstc2}.
The database contains information about 107 restaurants and their properties stored in the columns.
We include in brackets the number of different values for each column:
\begin{itemize}
%\begin{inparaenum}
    \item name (107),
    \item price range (4),
    \item area (7),
    \item food (25),
    \item address (101),
    \item phone (97),
    \item postcode (62).
% \end{inparaenum}\OD{tohle je ošklivý... buď dej do tabulky, nebo vyhoď, pokud by to žralo moc místa (uveď jen souhrnně největší-nejmenší)}
\end{itemize}

@@

\begin{figure}
\begin{center}
\includegraphics[height=25em]{gui-annotators-client}
\caption{Client annotation interface}
\end{center}
\vspace{-0.80em}
\label{fig:client}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=25em]{gui-annotators-system}
\caption{Operator annotation interface}\OD{v obrázcích bych se snažil nějak zvětšit text (menší okno prohlížeče před printscreenem? nějak upravené CSS? nevím... zas to asi nesmí být moc práce)}
\end{center}
\vspace{-0.80em}
\label{fig:operator}
\end{figure}

@@

In single job submission we let the workers append to each dialogue a~single response.
% Typically, we submit for annotation from twenty to thirty partial dialogues with different history lengths.
%Some conversations might be just initialized with the auto-generated greetings but most of them store multiple turns collected by CF contributors in the~previous submission.
% \OD{od “typically...” mi to přijde jako technikálie, která spíš mate}
Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
The workers are paid for every submitted response the same amount independently if they play client or operator role and they typically contribute to multiple conversation during one job submission.
The contributors are assigned roles randomly.

@@

% TODO describe how we started with 5 bootstrapped conversation with client role 5 without it and then mixed the partial with new one and resubmit them until the first conversations were marked as finished.

@@

We collected XY conversation with average length ZY.
During an average conversation \OP{2.4} tasks are requested and answered.
Typically in \OP{65} \% case the conversation is ended by the client
As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
\begin{table}
\begin{center}
\begin{tabular}{lrr}
\hline
Set   & \# Dialogues & \# Turns \\
\hline
% Joint  &  todo &  todo \\
% /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
% /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
Train  &   ? & ? \\
Dev &   ? & ? \\
Test &   ? & ? \\
\hline
\end{tabular}
\caption{Accuracy on development and test set}
\vspace{-2em}
\end{center}
\label{tab:props}
\end{table}

During the data collection process we discarded roughly \OP{40} \% of conversation.
We split the \OP{XYZ} collected conversation randomly into training, development and test set (see Table~\ref{tab:props}).

@@

We plan to increase the number of collected dialogues till the camera ready deadline to \OP{XYZU}.
We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only the database calls as additional supervision to the recorded responses.

>>>>

\maketitle
\OP{Fill missing values about the dataset collected so far} \\
\OP{new client interface image so the text is visible, fit to 8 pages}
\OP{grammar check} \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
We present a new dataset of human-human task-oriented conversations in the restaurant info domain for supervised training of autonomous systems. 
Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate that until camera ready deadline we will have more than seven hundreds dialogues. 
We aim at representing the conversation in such way that it is easy to train a system to replace an operator who provides information about the restaurants to clients.
In contrast to previously released datasets, our dataset contains easy to collect high-quality transcriptions of the client and operator actions during conversations.
We introduce a~very little overhead by collecting database calls in addition to the transcription of the conversation. 
In fact, we mimic very closely a~real situation in call centers where operators searches for answers through database user interface. 
On the other hand, just logging the calls to the task database provide us with information of the similar quality as it is contained in manually annotated dialogue state, just not annotated incrementally after each turn.
Tracking the database calls in task oriented systems together with conversation transcription should not introduce much overhead during data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.

@@

We used exactly the same database as provided for the DSTC2 challenge~\cite{henderson2014dstc2}.
The database contains information about 107 restaurants and their properties stored in the columns.
We include in brackets the number of different values for each column:
\begin{itemize}  % tabulku misto tohohle?
    \item name (107),
    \item price range (4),
    \item area (7),
    \item food (25),
    \item address (101),
    \item phone (97),
    \item postcode (62).
\end{itemize}

@@

\begin{figure}
\begin{center}
\includegraphics[height=30em]{gui-annotators-client}
\caption{Client annotation interface}
\end{center}
\vspace{-0.80em}
\label{fig:client}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=35em]{gui-annotators-system}
\caption{Operator annotation interface}
\end{center}
\vspace{-0.80em}
\label{fig:operator}
\end{figure}

@@

In single job submission we let the workers append to each dialogue a~single response.
Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
The workers are paid for every submitted response the same amount independently if they play client or operator role and they typically contribute to multiple conversation during one job submission.
The contributors are assigned roles randomly.

@@

@@

We just started to collect our dataset and so far we collected only 60 conversations.
The average length of a conversation is \OP{3.8} turns, meaning that the contributors and in both roles reply three times before the conversation is finished\footnote{First system reply is automatically generated and for some conversation even the first client reply is also initialized as described in Section~\ref{sec:async}}.
During an average conversation \OP{2.4} tasks are requested and \OP{1.9} answered.
Typically in \OP{65} \% case the conversation is ended by the client.
% As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
% \begin{table}
% \begin{center}
% \begin{tabular}{lrr}
% \hline
% Set   & \# Dialogues & \# Turns \\
% \hline
% % Joint  &  todo &  todo \\
% % /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
% % /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
% Train  &   ? & ? \\
% Dev &   ? & ? \\
% Test &   ? & ? \\
% \hline
% \end{tabular}
% \caption{Accuracy on development and test set}
% \vspace{-2em}
% \end{center}
% \label{tab:props}
% \end{table}

During the data collection process we discarded over \OP{40} \% of conversation because one of the utterances were mark as low quality.
Note that we discard only the low quality utterance and sufix of that conversation, the prefix is submitted for finishing the conversation in next rounds of jobs.
Once we will collect enough conversation we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).

@@

We plan to increase the number of collected dialogues till the camera ready deadline to 700 or more.
We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only the database calls as additional supervision to the recorded responses.
